\documentclass[12pt,landscape]{article}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{parskip}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{palatino}
\setlength{\columnsep}{2cm}
\pagestyle{empty}

\begin{document}

% ================= PAGE 1 =================
\begin{multicols}{2}
% ==== Left Column: Prayers of the Faithful ====
\section*{Prayers of the Faithful}

\textbf{Margaret:} \\
We pray for Rebekah and Chris as they begin their married life together. May their home be full of joy, love and laughter. May God grant them good health and peace of mind and may they always find great happiness and friendship in one another. We pray that they will be a source of kindness and unwavering support to each other throughout the adventures and challenges of life. Lord hear us.\\

\textbf{All:} \textit{Lord, graciously hear us.}

\vspace{1em}

\textbf{David:} \\
Let us pray for the friends and family of Rebekah and Chris, who have supported and loved them throughout their lives. May their relationships be enriched and may they continue to provide encouragement and companionship to the couple as they embark on this new journey together. Lord hear us.\\

\textbf{All:} \textit{Lord, graciously hear us.}

\vspace{1em}

\textbf{Tom:} \\
Let us remember those who are no longer with us but whose memories are a source of comfort and inspiration, and may they rest in peace, knowing the joy and happiness that Rebekah and Chris have found. Lord hear us.\\

\textbf{All:} \textit{Lord, graciously hear us.}

\columnbreak

% ==== Right Column: Liturgy of the Eucharist ====
\section*{Liturgy of the Eucharist}

\textbf{Offertory Procession}

\textbf{Fr Hyacinth:} \\
We now invite Claudine and Louise to bring the offertory gifts to the altar.

\vspace{0.5em}

\textbf{Fr Hyacinth:} \\
Pray, brothers and sisters, that my sacrifice and yours may be acceptable to God, the almighty Father.

\vspace{0.5em}

\textbf{All:} \\
\textit{May the Lord accept the sacrifice of your hands for the praise and glory of his name, for our good and the good of all his Church.}

\vspace{1em}

\textbf{Prayer over the Offerings}

\textbf{Fr Hyacinth:} \\
Lord, accept our offering for this newly married couple. In your fatherly love watch over them and protect Rebekah and Chris, whom you have united in marriage. We ask this through Christ our Lord.

\vspace{0.5em}

\textbf{All:} \textit{Amen.}

\end{multicols}

\newpage

% ================= PAGE 2 =================
\begin{multicols}{2}
% ==== Left Column: Eucharist Prayer ====
\section*{Eucharist Prayer}

\textbf{Fr Hyacinth:} The Lord be with you.\\
\textbf{All:} \textit{And with your spirit.}

\vspace{0.5em}

\textbf{Fr Hyacinth:} Lift up your hearts.\\
\textbf{All:} \textit{We lift them up to the Lord.}

\vspace{0.5em}

\textbf{Fr Hyacinth:} Let us give thanks to the Lord our God.\\
\textbf{All:} \textit{It is right and just.}

\vspace{1em}

\textbf{Fr Hyacinth:}\\
It is truly right and just, our duty and our salvation, always and everywhere to give you thanks, Lord, holy Father, almighty and eternal God.\\

For you willed that the human race, created by the gift of your goodness, should be raised to such high dignity that in the image of your love. For those you created out of charity you call to the law of charity without ceasing and grant them a share in your eternal charity. And so, the Sacrament of holy Matrimony, as the abiding sign of your own love, consecrates the love of man and woman, through Christ our Lord.

Through him, with the Angels and all the Saints, we sing the hymn of your praise, as without end we acclaim:

\vspace{1em}

\textbf{All:}\\
\textit{Holy, Holy, Holy Lord, God of hosts.\\
Heaven and earth are full of your glory,\\
Hosanna in the highest.\\
Blessed is he who comes in the name of the Lord.\\
Hosanna in the highest.}

\columnbreak

% ==== Right Column: Blessings and Rings ====
\section*{Blessing of the Rings}

\textbf{Fr Hyacinth:}\\
Lord, bless Rebekah and Chris, and consecrate their married life. May these rings be symbols of their faith in each other and reminders of their love. We make this prayer through Christ our Lord.

\vspace{0.5em}

\textbf{All:} \textit{Amen.}

\vspace{1em}

\section*{Exchange of Rings}

\textbf{Chris:}\\
Rebekah, wear this ring as a sign of our faithful love, in the name of The Father, and of The Son and of The Holy Spirit.

\vspace{1em}

\textbf{Rebekah:}\\
Christopher, wear this ring as a sign of our faithful love, in the name of The Father, and of The Son and of The Holy Spirit.

\vspace{1em}

\section*{Lighting of the Marriage Candle}

When Rebekah and Chris entered the Church today, they lit two candles to represent their individual lives and families from which they have now come. Now they are married, they light one candle together, which represents the joining of their lives as one in marriage. We pray for Rebekah and Chris and ask God to bless them in their new life together.

\vspace{1em}

\textit{Instrumental if you like.}

\end{multicols}

% ================= PAGE 3 =================
\newpage
\begin{multicols}{2}

% ==== Left Column: Declaration of Consent ====
\section*{Declaration of Consent}

\textbf{Fr Hyacinth:} Will you love and honour each other in marriage all the days of your life?\\
\textbf{Rebekah \& Chris:} We will.

\vspace{0.5em}

\textbf{Fr Hyacinth:} Are you willing to accept with love the children God may send you and bring them up in accordance with the law of Christ and his Church?\\
\textbf{Rebekah \& Chris:} We are.

\vspace{1em}

\textbf{Fr Hyacinth:} I invite you then to declare before God and his Church your consent to become husband and wife.

\vspace{0.5em}

\textbf{Fr Hyacinth:} Chris, do you take Rebekah as your wife\\
for better, for worse, for richer, for poorer,\\
in sickness and in health, all the days of your life?\\
\textbf{Chris:} I do

\vspace{0.5em}

\textbf{Fr Hyacinth:} Rebekah, do you take Chris as your husband\\
\textbf{Rebekah:} I do

\vspace{0.5em}

\textbf{Fr Hyacinth:} What God joins together man must not separate. May the Lord confirm the consent that you have given and enrich you with his blessings.

\textbf{All:} \textit{Amen.}

\columnbreak

% ==== Right Column: Mystery of Faith & Communion ====
\section*{Mystery of Faith}

\textbf{All:} \\
\textit{When we eat this Bread and drink this Cup, we proclaim your Death, O Lord, until you come again.}

\vspace{1em}

\textbf{Fr Hyacinth:} Through him, and with him, and in him, O God, almighty Father, in the unity of the Holy Spirit, all glory and honour is yours, for ever and ever.

\vspace{0.5em}

\textbf{All:} \textit{Amen.}

\vspace{1.5em}

\section*{Communion Rite}

\textbf{Fr Hyacinth:} At the Saviour's command and formed by divine teaching, we dare to say:

\vspace{0.5em}

\textbf{All:} \\
\textit{Our Father, who art in heaven,\\
hallowed be thy name.\\
Thy kingdom come, thy will be done,\\
on earth as it is in heaven.\\
Give us this day our daily bread,\\
and forgive us our trespasses,\\
as we forgive those who trespass against us;\\
and lead us not into temptation,\\
but deliver us from evil.\\
Amen.}

\end{multicols}

% ================= PAGE 4 =================
\newpage
\begin{multicols}{2}

% ==== Left Column: Nuptial Blessing ====
\section*{Nuptial Blessing}

\textbf{Fr Hyacinth:} \\
Let us ask God to bless Rebekah and Chris, now married in Christ and unite them in his love. God, our Father, creator of the universe, you made man and woman in your own likeness and blessed their union.

\vspace{0.5em}

We humbly pray to you for Rebekah and Chris, today united in the sacrament of marriage. May your blessing come upon them. May they find happiness in their love for each other, be blessed in their children and enrich the life of the Church.

May they praise you in their days of happiness and turn to you in times of sorrow.

May they know the joy of your help in their work, and the strength of your presence in their need. May they worship you with the Church and be your witness in the world. May you help them to be one in the company of their friends and may they reach at last the kingdom of heaven. We ask this through Christ our Lord.

\vspace{0.5em}
\textbf{All:} \textit{Amen.}

\columnbreak

% ==== Right Column: Gospel & Start of Rite ====
\section*{Gospel}

\textbf{Fr Hyacinth:} Jesus said to his disciples:

\vspace{0.5em}

\textit{“As the Father has loved me, so have I loved you. Now remain in my love.\\
If you keep my commands, you will remain in my love,\\
just as I have kept my Father’s commands and remain in his love.\\
I have told you this so that my joy may be in you and that your joy may be complete.\\
My command is this: Love each other as I have loved you.”}

\vspace{0.5em}

The Gospel of the Lord.\\
\textbf{All:} \textit{Thanks be to God.}

\vspace{1em}

\section*{Rite of Marriage}

\textbf{Fr Hyacinth:} \\
Dear Rebekah and Chris, you have come to this church so that the Lord may seal your love in the presence of the priest and this community. Christian marriage is a sacred union which enriches natural love. It binds those who enter it to be faithful to each other for life. It creates between them a bond that endures for life and cannot be broken; it demands that they love and honour each other, that they accept from God the children he may give them and bring them up in his love. To help them in their marriage the husband and wife receive the life-long grace of the sacrament. Is this your understanding of marriage?\\

\textbf{Rebekah \& Chris:} It is.

\vspace{0.5em}

\textbf{Fr Hyacinth:} Chris and Rebekah, you are about to celebrate this sacrament. Have you come here of your own free will and choice and without compulsion to marry each other?\\

\textbf{Rebekah \& Chris:} We have.

\end{multicols}

% ================= PAGE 5 =================
\newpage
\begin{multicols}{2}

% ==== Left Column: Reflection ====
\section*{Reflection}

\textbf{Stephen:}\\
\textit{I’ll Walk Beside You}

I’ll walk beside you through the world today\\
While dreams and songs and flowers bless your way.\\
I’ll look into your eyes and hold your hand\\
I’ll walk beside you through the golden land,\\

I’ll walk beside you through the world tonight\\
Beneath the starry skies ablaze with light,\\
Within your soul love’s tender words I’ll hide\\
I’ll walk beside you through the eventide,\\

I’ll walk beside you through the passing years\\
Through days of cloud and sunshine, joy and tears\\
And when the great call comes, the sunset gleams\\
I’ll walk beside you to the land of dreams.

\columnbreak

% ==== Right Column: The Liturgy of the Word ====
\section*{The Liturgy of the Word}

\textbf{First Reading}

\textbf{Claire:}\\
A Reading from the Book of Sirach.\\
A loving partner is a safe shelter, whoever finds one has found a rare treasure. A loving partner is something beyond price, there is no measuring their worth. A loving partner is a life-saving remedy, and those who respect their Lord find true love. For as a person is, so is their loved one.

\textbf{The word of the Lord.}\\
\textbf{All:} \textit{Thanks be to God.}

\vspace{1em}

\textbf{Responsorial Psalm (sung)}

\end{multicols}

% ================= PAGE 6 =================
\newpage
\begin{multicols}{2}

% ==== Left Column: Second Reading ====
\section*{Second Reading}

\textbf{Stephanie:}\\
A Reading from the Song of Solomon\\
My beloved speaks and says to me: “Arise, my love, my fair one, and come away; for now the winter is past, the rain is over and gone. The flowers appear on the earth; the time of singing has come, and the voice of the turtle-dove is heard in our land. The fig tree puts forth its figs, and the vines are in blossom; they give forth fragrance. Arise, my love, my fair one, and come away.” 

Set me as a seal upon your heart, as a seal upon your arm; for love is strong as death, passion fierce as the grave. Its flashes are flashes of fire, a raging flame. Many waters cannot quench love, neither can floods drown it. If one offered for love all the wealth of one’s house, it would be utterly scorned.

\textbf{The word of the Lord.}\\
\textbf{All:} \textit{Thanks be to God.}

\vspace{1em}

\textbf{Gospel Acclamation (sung)}

\columnbreak

% ==== Right Column: Gospel & Communion ====
\section*{Gospel}

\textbf{Fr Hyacinth:}\\
A reading from the holy Gospel according to John.

\textbf{All:} \textit{Glory to you, O Lord.}

\vspace{1em}

\textbf{Fr Hyacinth:} The peace of the Lord be with you.\\
\textbf{All:} \textit{And with your spirit.}

\vspace{0.5em}

\textbf{Fr Hyacinth:} Let us offer each other the sign of peace.

\vspace{1em}
\textbf{All:}\\
\textit{Lamb of God, you take away the sins of the world: have mercy on us.\\
Lamb of God, you take away the sins of the world: have mercy on us.\\
Lamb of God, you take away the sins of the world: grant us peace.}

\vspace{1em}
\textbf{Fr Hyacinth:}\\
Behold the Lamb of God,\\
behold him who takes away the sins of the world.\\
Blessed are those called to the supper of the Lamb.

\vspace{0.5em}
\textbf{All:} \textit{Lord, I am not worthy that you should enter under my roof, but only say the word and my soul shall be healed.}

\vspace{1em}
\textbf{The Distribution of Holy Communion}

\end{multicols}

% ================= PAGE 7 =================
\newpage
\begin{multicols}{2}

% ---- Left Column: The Gloria, Opening Prayer, Prayer after Communion ----
\section*{The Gloria}
\textbf{All:}\\
Glory to God in the highest,\\
and on earth peace to people of good will.\\[0.5em]
We praise you, we bless you, we adore you, we glorify you, we give you thanks for your great glory,\\
Lord God, heavenly King, O God, almighty Father.\\[0.5em]
Lord Jesus Christ, Only Begotten Son, Lord God, Lamb of God, Son of the Father,\\
you take away the sins of the world, have mercy on us;\\
You take away the sins of the world, receive our prayer;\\
you are seated at the right hand of the Father: have mercy on us.\\[0.5em]
For you alone are the Holy One, you alone are the Lord, you alone are the Most High,\\
Jesus Christ, with the Holy Spirit, in the glory of God the Father.\\[0.5em]
\textbf{All:} Amen.

\section*{Opening Prayer}
\textbf{Fr Hyacinth:} Let us pray. Father, you have made this bond of marriage a holy mystery, a symbol of Christ's love for his Church.\\[0.5em]
Hear our prayers for Rebekah and Chris. With faith in you and in each other they pledge their love today. May their lives always bear witness to the reality of that love. We ask this through our Lord Jesus Christ, your Son, who lives and reigns with you and the Holy Spirit, one God, for ever and ever.\\[0.5em]
\textbf{All:} Amen.

\section*{Prayer after Communion}
\textbf{Fr Hyacinth:} Let us pray. Lord, we who have shared the food of your table pray for our friends Rebekah and Chris, whom you have joined together in marriage. Protect them, keep them close to you always. May their love for each other proclaim to all the world their faith in you. We ask this through Christ our Lord.\\[0.5em]
\textbf{All:} Amen.

\columnbreak

% ---- Right Column: Concluding Rite & Blessing ----
\section*{Concluding Rite}
\textbf{Fr Hyacinth:} The Lord be with you.\\
\textbf{All:} And with your spirit.

\section*{Blessing}
\textbf{Fr Hyacinth:} May God, the eternal Father, keep you steadfast in your love.\\[0.5em]
\textbf{All:} Amen.

\textbf{Fr Hyacinth:} May you be blessed in your children, have solace in your friends, and enjoy true peace with everyone.\\[0.5em]
\textbf{All:} Amen.

\textbf{Fr Hyacinth:} May God bless all of you, who are gathered here today, in the name of the Father, and the Son, and the Holy Spirit.\\[0.5em]
\textbf{All:} Amen.

\end{multicols}

% ================= PAGE 8 =================
\newpage
\begin{multicols}{2}

% ---- Left Column: Dismissal, Signing of the Register, Recessional ----
\section*{Dismissal}
\textbf{Fr Hyacinth:} Go in peace to love and serve the Lord.\\[0.5em]
\textbf{All:} Thanks be to God.

\section*{Signing of the Register}
Piece of music in the background (not too long).

\section*{Recessional}
Your choice: walking down the aisle.

\columnbreak

% ---- Right Column: Confession and Prayers for Mercy ----
\section*{Confession}
\textbf{All:}\\
I confess to almighty God and to you, my brothers and sisters, that I have greatly sinned, in my thoughts and in my words, in what I have done and in what I have failed to do, through my fault, through my fault, through my most grievous fault; therefore I ask blessed Mary ever-Virgin, all the Angels and Saints, and you, my brothers and sisters, to pray for me to the Lord our God.

\section*{Prayers for Mercy}
\textbf{Fr Hyacinth:} May almighty God have mercy on us, forgive us our sins, and bring us to everlasting life.\\[0.5em]
\textbf{All:} Amen.

\textbf{Fr Hyacinth:} Lord have mercy.\\
\textbf{All:} Lord have mercy.

\textbf{Fr Hyacinth:} Christ have mercy.\\
\textbf{All:} Christ have mercy.

\textbf{Fr Hyacinth:} Lord have mercy.\\
\textbf{All:} Lord have mercy.

\end{multicols}

% ================= PAGE 9 =================
\newpage
\begin{multicols}{2}

% ---- Left Column: Bridal Procession, Greeting and Welcome, Lighting of the Candles, Penitential Rite, Thank You ----
\section*{Bridal Procession}

\textbf{Greeting and Welcome}

\textbf{Fr Hyacinth:} Fill us with your love, O Lord, and we will sing for joy all our days. In the name of the Father and of the Son and of the Holy Spirit.\\[0.5em]
\textbf{All:} Amen.\\[1em]

\textbf{Fr Hyacinth:} The Lord be with you.\\
\textbf{All:} And with your spirit.\\[1em]

\section*{Lighting of the Candles}

Rebekah and Chris light two candles at the altar representing their presence here today as two single individuals.\\[0.5em]
\textit{(Instrumental, if you like)}\\[1em]

\section*{Penitential Rite}

\textbf{Fr Hyacinth:} As we offer this nuptial mass for Rebekah and Chris, let all who are here today renew our love, loyalty, and fidelity to God and to one another. Let us prepare ourselves to celebrate the sacred mysteries by calling to mind our sins.

\vspace{1em}

\section*{Thank You}

We warmly welcome each of you here today and thank you for joining us to celebrate this beautiful moment in our lives.\\[0.5em]
To our parents, families, and friends who have supported and encouraged us through every step of our journey—your generosity, love, and guidance have led us to this joyful day, and we are forever grateful.\\[0.5em]
Today is a celebration of our love, and we couldn't be happier to share it with all of you. Thank you for making this truly unforgettable.

\columnbreak

% ---- Right Column: (Optional additional notes or leave empty) ----
% If you wish, add any additional text here for the right column.
\end{multicols}

% ================= PAGE 10 =================
\newpage
\begin{multicols}{2}

% ---- Left Column: intentionally left empty ----
\vspace*{\fill}
\mbox{}
\vspace*{\fill}

\columnbreak

% ---- Right Column: Roles and Names Table ----
\section*{Ceremony Participants}

\smallskip
\begin{tabular}{@{}p{4cm}p{8cm}@{}}
\textbf{Bride} & Rebekah Murphy \\[1ex]
\textbf{Groom} & Chris Rowberry \\[1ex]
\textbf{Celebrant} & Fr. Hyacinth Nwakuna \\[1ex]
\textbf{Maid of Honour} & Jessica Murphy \\[1ex]
\textbf{Bridesmaids} & Imogen Frame \\[1ex]
\textbf{Best Man} & Sarah McCarthy, Steven Peacock \\[1ex]
\textbf{Groomsmen} & Andrew Pereira, Nick Woods,\\[0.5ex]
             & Hugh Montgomery-Pott, Jake Vials,\\[0.5ex]
             & Neil Collins \\[1ex]
\textbf{Ushers} & Conor Tripp \\[1ex]
\textbf{Readers} & Eric Tyrrell, Claire Wylde \\[1ex]
\textbf{Prayers of the Faithful} & Stephanie Frame, Margaret Leonard,\\[0.5ex]
             & David Frame, Tom Murphy \\[1ex]
\textbf{Offertory Procession} & Claudine Craig, Louise Murphy \\[1ex]
\textbf{Reflection \& Music} & Stephen Murphy, Barbara Galvin \\
\end{tabular}

\end{multicols}

\end{document}